Client-Side Indexes for Fast Full-Text Searching

### 2014-12-10 paper/paper.tex
add to implementation

@@

We created Lucy.js in JavaScript, as the IndexedDB API is also in JavaScript.

>>>>

The default rank that we implement is

@@

We created Lucy.js in JavaScript, as the IndexedDB API is also in JavaScript. The code consists of three main files - \texttt{lucy.js}, \texttt{invindex.js}, and \texttt{trieindex.js} that the developer must include in their HTML file. The user should also additionally add one of the \texttt{<language>\_stopwords.js} files in order to pick a language to check stopwords on.

The file \texttt{lucy.js} contains a static class called \texttt{Lucy} which holds various text processing functions that the different indexes use. There is also an extension of \texttt{IDBRequest} called \texttt{IDBIndexRequest} that provides the same behavior, only for our full-text indexes. Finally, there are a set of functions that intercept functions of \texttt{IDBObjectStore}. When a user calls \texttt{create\_index} or \texttt{index}, if they are creating or referring to a full-text index we direct the function to one of our index implementations. When a user calls \texttt{add},  \texttt{delete}, or \texttt{put} on an object store that has a full-text index, we additionally add the item to our indexes.
